%\chapter{Publications}
\chapter{Foreword}

The contributions presented in this thesis have been published at various workshops, conferences and journals. Firstly, I list the most important publications that directly contribute to this thesis with regard to \emph{semantic annotation}, \emph{semantic search} and \emph{cross-lingual semantics}, as follows:

\forceindent\textbf{Semantic Annotation}
\begin{itemize}
    \item Lei Zhang, Achim Rettinger, Patrick Philipp: Context-Aware Entity Disambiguation in Text Using Markov Chains. In \emph{Proceedings of the 2016 IEEE/WIC/ACM International Conferences on Web Intelligence (WI 2016), Omaha, Nebraska, USA, October 13-16, 2016.}~\cite{wi2016}
%    \textbf{(Long Paper)}
    \item Lei Zhang, Cong Liu, Achim Rettinger: A Topic-Sensitive Model for Salient Entity Linking. In \emph{Proceedings of the 3rd International Workshop on Linked Data for Information Extraction (LD4IE) co-located with the 14th International Semantic Web Conference (ISWC 2015), Bethlehem, Pennsylvania, USA, October 11-15, 2015.}~\cite{DBLP:conf/semweb/ZhangLR15}
%    \textbf{(Long Paper)}
\end{itemize}

\forceindent\textbf{Semantic Search}
\begin{itemize}
    \item Lei Zhang, Achim Rettinger, Ji Zhang: A Probabilistic Model for Time-Aware Entity Recommendation. In \emph{Proceedings of the 15th International Semantic Web Conference (ISWC 2016), Kobe, Japan, October 17-21, 2016.}~\cite{DBLP:conf/semweb/ZhangRZ16a}
%    \textbf{(Long Paper)}
    \textbf{Best Student Research Paper}
    \item Lei Zhang, Thanh Tran, Achim Rettinger: Probabilistic Query Rewriting for Efficient and Effective Keyword Search on Graph Data. In \emph{Proceedings of the VLDB Endowment of the 39th International Conference on Very Large Data Bases (VLDB 2013) Volume 6, Number 14, September 2013.}~\cite{DBLP:journals/pvldb/0007TR13}
%    \textbf{(Long Paper)}
\end{itemize}

\forceindent\textbf{Cross-lingual Semantics}
\begin{itemize}
    \item  Lei Zhang, Achim Rettinger, Ji Zhang: A Knowledge Base Approach to Cross-lingual Keyword Query Interpretation. In \emph{Proceedings of the 15th International Semantic Web Conference (ISWC 2016), Kobe, Japan, October 17-21, 2016.}~\cite{DBLP:conf/semweb/ZhangRZ16}
%    \textbf{(Long Paper)}
    \item Lei Zhang, Michael Färber, Achim Rettinger: XKnowSearch! Exploiting Knowledge Bases for Entity-based Cross-lingual Information Retrieval. In \emph{Proceedings of the 25th ACM International Conference on Information and Knowledge Management (CIKM 2016), Indianapolis, USA, October 24-28, 2016.}~\cite{DBLP:conf/cikm/Zhang16}
%    \textbf{(Demo Paper)}
    \item Lei Zhang, Achim Rettinger: X-LiSA: Cross-lingual Semantic Annotation. In \emph{ Proceedings of the VLDB Endowment of the 40th International Conference on Very Large Data Bases (VLDB 2014), Volume 7, Number 13, August 2014.}~\cite{xlisa}
%    \textbf{(Demo Paper)}
    \item Lei Zhang, Michael Färber, Achim Rettinger: xLiD-Lexica: Cross-lingual Linked Data Lexica. In \emph{Proceedings of the 9th International Conference on Language Resources and Evaluation (LREC 2014), Reykjavik, Iceland, May 26-31, 2014.}~\cite{Zhang2014}
%    \textbf{(Short Paper)}
    \item Lei Zhang, Achim Rettinger, Steffen Thoma: Bridging the Gap between Cross-lingual NLP and DBpedia by Exploiting Wikipedia. In \emph{Proceedings of the NLP{\&}DBpedia workshop co-located with the 13th International Semantic Web Conference (ISWC 2014), Riva del Garda, Italy, October 19-23, 2014.}~\cite{zhang2014btgbcnadbew}
\end{itemize}

In the course of writing this thesis, I have published several other papers, which helped me to shape the focus of the present work. They could be considered as related work:  

\forceindent\textbf{Other Publications}
\begin{itemize}
    \item Lei Zhang, Michael Färber, Andreas Thalhammer, Aditya Mogadala, Achim Rettinger: Exploiting Knowledge Bases for Multilingual and Cross-lingual Semantic Annotation and Search. \emph{The Semantic Web Challenge co-located with the 14th International Semantic Web Conference (SWC 2015), Bethlehem, Pennsylvania, USA, October 11-15, 2015.}~\cite{zhang2015swc} 
    \textbf{2nd Prize Winner}
    \item Lei Zhang, Thanh Tran, Achim Rettinger: A Theoretical Analysis of Cross-lingual Semantic Relatedness in Vector Space Models. In \emph{Proceedings of the 2015 International Conference on The Theory of Information Retrieval (ICTIR 2015), Northampton, Massachusetts, USA, September 27-30, 2015.}~\cite{DBLP:conf/ictir/0007TR15}
%    \textbf{(Long Paper)}
    \item Lei Zhang, Yunpeng Dong, Achim Rettinger: Towards Entity Correctness, Completeness and Emergence for Entity Recognition. In \emph{Proceedings of the 24th International Conference on World Wide Web Companion (WWW 2015), Florence, Italy, May 18-22, 2015.}~\cite{DBLP:conf/www/ZhangDR15}
%%    \textbf{(Short Paper)}
    \item Lei Zhang, Wentao Chen, Thanh Tran, Achim Rettinger: Time-Aware Entity Search in DBpedia. \emph{The Semantic Web: ESWC 2015 Satellite Events, Portorož, Slovenia, May 31 - June 4, 2015.}~\cite{DBLP:conf/esws/0034CTR15}
%    \textbf{(Short Paper)}
    \item Thanh Tran, Lei Zhang: Keyword Query Routing. \emph{IEEE Transactions on Knowledge and Data Engineering (TKDE), Volume 26, Number 2, February 2014.}~\cite{DBLP:journals/tkde/Tran014}
%    \textbf{(Long Paper)}
    \item Lei Zhang, Achim Rettinger: Semantic Annotation, Analysis and Comparison: A Multilingual and Cross-lingual Text Analytics Toolkit. In \emph{Proceedings of the 14th Conference of the European Chapter of the Association for Computational Linguistics (EACL 2014), Gothenburg, Sweden, April 26-30, 2014.}~\cite{DBLP:conf/eacl/ZhangR14}
%    \textbf{(Demo Paper)}
    \item Xavier Carreras, Lluís Padró, Lei Zhang, Achim Rettinger, Zhixing Li, Esteban García-Cuesta, Zeljko Agic, Bozo Bekavac, Blaz Fortuna, Tadej Stajner: XLike Project Language Analysis Services. In \emph{Proceedings of the 14th Conference of the European Chapter of the Association for Computational Linguistics (EACL 2014), Gothenburg, Sweden, April 26-30, 2014.}~\cite{DBLP:conf/eacl/CarrerasP0RLGABFS14}
%    \textbf{(Demo Paper)}
    \item Michael Färber, Lei Zhang, Achim Rettinger: Kuphi - an Investigation Tool for Searching for and via Semantic Relations. \emph{The Semantic Web: ESWC 2014 Satellite Events, Anissaras, Crete, Greece, May 25-29, 2014.}~\cite{DBLP:conf/esws/Farber0R14}
%    \textbf{(Demo Paper)}
    \item 	Achim Rettinger, Lei Zhang, Dasa Berovic, Danijela Merkler, Matea Srebacic, Marko Tadic: RECSA: Resource for Evaluating Cross-lingual Semantic Annotation. In \emph{Proceedings of the 9th International Conference on Language Resources and Evaluation (LREC 2014), Reykjavik, Iceland, May 26-31, 2014.}~\cite{DBLP:conf/lrec/RettingerZBMST14}
%    \textbf{(Short Paper)}
    \item Lei Zhang, Michael Färber, Thanh Tran, Achim Rettinger: Exploiting Semantic Annotations for Entity-based Information Retrieval. In \emph{Proceedings of the ISWC 2014 Posters \& Demonstrations Track a track within the 13th International Semantic Web Conference (ISWC 2014), Riva del Garda, Italy, October 19-23, 2014.}~\cite{DBLP:conf/semweb/0007FTR14}
%    \textbf{(Short Paper)}
    \item Lei Zhang, Achim Rettinger, Michael Färber, Marko Tadic: A Comparative Evaluation of Cross-Lingual Text Annotation Techniques. \emph{Information Access Evaluation. Multilinguality, Multimodality, and Visualization - 4th International Conference of the CLEF Initiative (CLEF 2013), Valencia, Spain, September 23-26, 2013.}~\cite{DBLP:conf/clef/ZhangRFT13}
%    \textbf{(Long Paper)}
    \item Thanh Tran, Lei Zhang, Rudi Studer: Summary Models for Routing Keywords to Linked Data Sources. In \emph{Proceedings of the 9th International Semantic Web Conference (ISWC 2010), Shanghai, China, November 7-11, 2010.}~\cite{DBLP:conf/semweb/TranZS10}
%    \textbf{(Long Paper)}
\end{itemize}


%\begin{itemize}
%    \item  Lei Zhang, Achim Rettinger, Ji Zhang: A Knowledge Base Approach to Cross-lingual Keyword Query Interpretation. In \emph{Proceedings of the 15th International Semantic Web Conference (ISWC 2016), Kobe, Japan, October 17-21, 2016.}~\cite{DBLP:conf/semweb/ZhangRZ16}
%%    \textbf{(Long Paper)}
%    
%    \item Lei Zhang, Achim Rettinger, Ji Zhang: A Probabilistic Model for Time-Aware Entity Recommendation. In \emph{Proceedings of the 15th International Semantic Web Conference (ISWC 2016), Kobe, Japan, October 17-21, 2016.}~\cite{DBLP:conf/semweb/ZhangRZ16a}
%%    \textbf{(Long Paper)}
%    \textbf{Best Student Research Paper}
%    
%    \item Lei Zhang, Achim Rettinger, Patrick Philipp: Context-Aware Entity Disambiguation in Text Using Markov Chains. In \emph{Proceedings of the 2016 IEEE/WIC/ACM International Conferences on Web Intelligence (WI 2016), Omaha, Nebraska, USA, October 13-16, 2016.}~\cite{wi2016}
%%    \textbf{(Long Paper)}
%    
%    \item Lei Zhang, Michael Färber, Achim Rettinger: XKnowSearch! Exploiting Knowledge Bases for Entity-based Cross-lingual Information Retrieval. In \emph{Proceedings of the 25th ACM International Conference on Information and Knowledge Management (CIKM 2016), Indianapolis, USA, October 24-28, 2016.}~\cite{DBLP:conf/cikm/Zhang16}
%%    \textbf{(Demo Paper)}
%    
%    \item Lei Zhang, Michael Färber, Andreas Thalhammer, Aditya Mogadala, Achim Rettinger: Exploiting Knowledge Bases for Multilingual and Cross-lingual Semantic Annotation and Search. \emph{The Semantic Web Challenge co-located with the 14th International Semantic Web Conference (SWC 2015), Bethlehem, Pennsylvania, USA, October 11-15, 2015.}~\cite{zhang2015swc} 
%    \textbf{2nd Prize Winner}
%    
%    \item Lei Zhang, Thanh Tran, Achim Rettinger: A Theoretical Analysis of Cross-lingual Semantic Relatedness in Vector Space Models. In \emph{Proceedings of the 2015 International Conference on The Theory of Information Retrieval (ICTIR 2015), Northampton, Massachusetts, USA, September 27-30, 2015.}~\cite{DBLP:conf/ictir/0007TR15}
%%    \textbf{(Long Paper)}
%    
%    \item Lei Zhang, Cong Liu, Achim Rettinger: A Topic-Sensitive Model for Salient Entity Linking. In \emph{Proceedings of the 3rd International Workshop on Linked Data for Information Extraction (LD4IE) co-located with the 14th International Semantic Web Conference (ISWC 2015), Bethlehem, Pennsylvania, USA, October 11-15, 2015.}~\cite{DBLP:conf/semweb/ZhangLR15}
%%    \textbf{(Long Paper)}
%    
%    \item Lei Zhang, Yunpeng Dong, Achim Rettinger: Towards Entity Correctness, Completeness and Emergence for Entity Recognition. In \emph{Proceedings of the 24th International Conference on World Wide Web Companion (WWW 2015), Florence, Italy, May 18-22, 2015.}~\cite{DBLP:conf/www/ZhangDR15}
%%%    \textbf{(Short Paper)}
%    
%    \item Lei Zhang, Wentao Chen, Thanh Tran, Achim Rettinger: Time-Aware Entity Search in DBpedia. \emph{The Semantic Web: ESWC 2015 Satellite Events, Portorož, Slovenia, May 31 - June 4, 2015.}~\cite{DBLP:conf/esws/0034CTR15}
%%    \textbf{(Short Paper)}
%    
%    \item Lei Zhang, Achim Rettinger: X-LiSA: Cross-lingual Semantic Annotation. In \emph{ Proceedings of the VLDB Endowment of the 40th International Conference on Very Large Data Bases (VLDB 2014), Volume 7, Number 13, August 2014.}~\cite{xlisa}
%%    \textbf{(Demo Paper)}
%    
%    \item Thanh Tran, Lei Zhang: Keyword Query Routing. \emph{IEEE Transactions on Knowledge and Data Engineering (TKDE), Volume 26, Number 2, February 2014.}~\cite{DBLP:journals/tkde/Tran014}
%%    \textbf{(Long Paper)}
%    
%    \item Lei Zhang, Achim Rettinger: Semantic Annotation, Analysis and Comparison: A Multilingual and Cross-lingual Text Analytics Toolkit. In \emph{Proceedings of the 14th Conference of the European Chapter of the Association for Computational Linguistics (EACL 2014), Gothenburg, Sweden, April 26-30, 2014.}~\cite{DBLP:conf/eacl/ZhangR14}
%%    \textbf{(Demo Paper)}
%    
%    \item Xavier Carreras, Lluís Padró, Lei Zhang, Achim Rettinger, Zhixing Li, Esteban García-Cuesta, Zeljko Agic, Bozo Bekavac, Blaz Fortuna, Tadej Stajner: XLike Project Language Analysis Services. In \emph{Proceedings of the 14th Conference of the European Chapter of the Association for Computational Linguistics (EACL 2014), Gothenburg, Sweden, April 26-30, 2014.}~\cite{DBLP:conf/eacl/CarrerasP0RLGABFS14}
%%    \textbf{(Demo Paper)}
%    
%    \item Michael Färber, Lei Zhang, Achim Rettinger: Kuphi - an Investigation Tool for Searching for and via Semantic Relations. \emph{The Semantic Web: ESWC 2014 Satellite Events, Anissaras, Crete, Greece, May 25-29, 2014.}~\cite{DBLP:conf/esws/Farber0R14}
%%    \textbf{(Demo Paper)}
%    
%    \item Lei Zhang, Michael Färber, Achim Rettinger: xLiD-Lexica: Cross-lingual Linked Data Lexica. In \emph{Proceedings of the 9th International Conference on Language Resources and Evaluation (LREC 2014), Reykjavik, Iceland, May 26-31, 2014.}~\cite{Zhang2014}
%%    \textbf{(Short Paper)}
%    
%    \item 	Achim Rettinger, Lei Zhang, Dasa Berovic, Danijela Merkler, Matea Srebacic, Marko Tadic: RECSA: Resource for Evaluating Cross-lingual Semantic Annotation. In \emph{Proceedings of the 9th International Conference on Language Resources and Evaluation (LREC 2014), Reykjavik, Iceland, May 26-31, 2014.}~\cite{DBLP:conf/lrec/RettingerZBMST14}
%%    \textbf{(Short Paper)}
%    
%    \item Lei Zhang, Michael Färber, Thanh Tran, Achim Rettinger: Exploiting Semantic Annotations for Entity-based Information Retrieval. In \emph{Proceedings of the ISWC 2014 Posters \& Demonstrations Track a track within the 13th International Semantic Web Conference (ISWC 2014), Riva del Garda, Italy, October 19-23, 2014.}~\cite{DBLP:conf/semweb/0007FTR14}
%%    \textbf{(Short Paper)}
%    
%    \item Lei Zhang, Achim Rettinger, Steffen Thoma: Bridging the Gap between Cross-lingual NLP and DBpedia by Exploiting Wikipedia. In \emph{Proceedings of the NLP{\&}DBpedia workshop co-located with the 13th International Semantic Web Conference (ISWC 2014), Riva del Garda, Italy, October 19-23, 2014.}~\cite{zhang2014btgbcnadbew}
%    
%    \item Lei Zhang, Thanh Tran, Achim Rettinger: Probabilistic Query Rewriting for Efficient and Effective Keyword Search on Graph Data. In \emph{Proceedings of the VLDB Endowment of the 39th International Conference on Very Large Data Bases (VLDB 2013) Volume 6, Number 14, September 2013.}~\cite{DBLP:journals/pvldb/0007TR13}
%%    \textbf{(Long Paper)}
%    
%    \item Lei Zhang, Achim Rettinger, Michael Färber, Marko Tadic: A Comparative Evaluation of Cross-Lingual Text Annotation Techniques. \emph{Information Access Evaluation. Multilinguality, Multimodality, and Visualization - 4th International Conference of the CLEF Initiative (CLEF 2013), Valencia, Spain, September 23-26, 2013.}~\cite{DBLP:conf/clef/ZhangRFT13}
%%    \textbf{(Long Paper)}
%    
%    \item Thanh Tran, Lei Zhang, Rudi Studer: Summary Models for Routing Keywords to Linked Data Sources. In \emph{Proceedings of the 9th International Semantic Web Conference (ISWC 2010), Shanghai, China, November 7-11, 2010.}~\cite{DBLP:conf/semweb/TranZS10}
%%    \textbf{(Long Paper)}
% 
%\end{itemize}
